|

### 2024-08-11 doc/paper.qmd
latex formatting

def prep_latex_table(df, caption=None, label=None, fontsize='\\fontsize{11}{13}\\selectfont'):
    df = escape_special_characters(df.reset_index(drop=True))  # Drop the index column from output tables for better readability
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)
    latex_table = df.to_latex(
        column_format=column_format,
        index=False, 
        float_format=custom_float_format,
    )
    latex_table_lines = [
        "\\begin{table}[htbp]",
        "\\centering",
        fontsize,  # Set font size for the table
        latex_table,
        f"\\caption{{{caption}}}" if caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

print(prep_latex_table(
    em_results['final_combined_table'], 
    caption='Replicated table - Country scores for earnings management measures (Sorted by aggregate earnings management)',
    label='tab:final_combined_table'
))
```

>>>>

def prep_latex_table(df, caption=None, label=None, fontsize='\\fontsize{11}{13}\\selectfont', description=None):
    df = escape_special_characters(df.reset_index(drop=True))  # Drop the index column from output tables for better readability
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)

    latex_table = df.to_latex(
        column_format=column_format,
        index=False, 
        float_format=custom_float_format,
        escape=False  # Important to disable escaping so LaTeX commands in column names are respected
    )

    # Construct description to the table
    full_caption = f"{caption}\\\\\n\\textnormal{{{description}}}" if description else caption

    latex_table_lines = [
        "\\begin{table}[htbp]",
        "\\centering",
        fontsize,  # Set font size for the table
        latex_table,
        f"\\caption{{{full_caption}}}" if full_caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

# Rename the columns to ensure consistency with paper
em_results['final_combined_table'].rename(columns={
    'item6026': 'Country',
    'EM1': 'EM1 (−)',
    'EM2': 'EM2 (−)',
    'EM3': 'EM3 (+)',
    'EM4': 'EM4 (+)',
    'Aggregate_EM_Score': 'Aggregate EM score'
}, inplace=True)

print(prep_latex_table(
    em_results['final_combined_table'], 
    caption='Replicated table - Country scores for earnings management measures (Sorted by aggregate earnings management)',
    label='tab:final_combined_table',
    description = (
    "\\fontsize{10pt}{12pt}\\selectfont " 
    "The variables are computed from 123,469 firm-year observations for fiscal years 1990 to 1999 across 31 countries and 18,040 non-financial firms. Data are obtained from the Worldscope Database (July 2024 version). The definitions and calculations of EM1-4, as well as the aggregate score, are thoroughly presented in Section 4. The sign in the column heading indicates whether higher scores for the respective EM measure imply more earnings management (+) or less earnings management (−)."
    )

))
```
